### 2015-10-07 untitled.tex
text for original schedule
revise caption
revise caption…

\textbf{XXX TODO:} It would be nice to show a schedule for the uncontrolled example.\textbf{XXX}

The period enforcer algorithm determines for each segment (i.e., for each converted single-segment deferrable task) an \emph{eligibility time}. If a segment resumes (i.e., a job of a single-segment deferrable task arrives) before its eligibility time, the execution of the segment (i.e., the single-segment job) is delayed until the eligibility time is reached.

@@

In the context of the period enforcer, we consequently observe that the only existing solution to derive the \emph{precise} bound $W_k^{j}$ (and hence $R_k^j$), due to Nelissen et al.\ \cite{ecrts15nelissen},  has exponential time complexity. Furthermore, as demonstrated with the example shown in Figure~\ref{fig:example}, even if the conversion is done precisely, the transformed single-segment deferrable task set can admit more pessimism than the original self-suspending task set with respect to schedulability.

>>>>

Let's release these two tasks periodically, starting from time $0$. The fixed-priority schedule is presented in Figure \ref{fig:example-original}.
The period enforcer algorithm determines for each segment (i.e., for each converted single-segment deferrable task) an \emph{eligibility time}. If a segment resumes (i.e., a job of a single-segment deferrable task arrives) before its eligibility time, the execution of the segment (i.e., the single-segment job) is delayed until the eligibility time is reached.

@@

In the context of the period enforcer, we consequently observe that the only existing solution to derive the \emph{precise} bound $W_k^{j}$ (and hence $R_k^j$), due to Nelissen et al.\ \cite{ecrts15nelissen},  has exponential time complexity (even for the special case above). Furthermore, as demonstrated with the example shown in Figure~\ref{fig:example}, even if the conversion is done precisely, the transformed single-segment deferrable task set can admit more pessimism than the original self-suspending task set with respect to schedulability.
